Put Title here

### 2018-12-13 General WLD combinatorics.tex
added a def of neighbourhood in the graph theory sense in a footnote

By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the \hlfix{neighbourhoods}{neigbors? Or a separate definition of neigborhood?} of the $v_i$ is the neighbourhood of $v$.

>>>>

By \emph{splitting} a vertex $v$ we will mean replacing $v$ by new vertice $v_1, v_2,\ldots, v_{\text{deg}(v)}$ such that each $v_i$ has exactly one neighbour and the union of the of the $v_i$ is the neighbourhood\footnote{The neighbourhood of a vertex is the set of adjacent vertices} of $v$.
